Early environmental conditions do not impact behavioural flexibility in an invasive and non-invasive lizard species

### 2024-03-16 ms.qmd
Updates

knitr::include_graphics("./Others/BEHFLEX_FIG_1")

@@

#### Slopes estimates per treatment and species for the original database

@@

#### Slopes estimates per treatment and species employing only those individuals that passed a learning criterion of 80% correct choices in the last 10 trials of the associative task

>>>>

knitr::include_graphics("./Others/BEHFLEX_FIG_1.png")

@@

@@
